Badʾu-l-masīri fī taʾrīḫi-t-tafsīri--An Exploratory Data Analysis of 17 Tafāsīr From the Early 8th to the Late 14th

### 2016-12-20 tafaseer_group/03_results/paper.rmd
bah

Our attempt at determining which verses enjoyed more consideration from the *mufassirūn* began with calculating the word count of every section of the tafsir that was commenting on a specific verse and dividing that number by the total word count of the *tafsīr*. It was our belief that increased attention on a verse was indicative of some sort of importance to the *mufassir*. Importance might not necessarily mean that the *mufassir* had an increased affinity for the values or instructions espoused in the verse. A *mufassir* might have believed that an obscure verse required elucidation to make its message comprehensible to the Muslim layman and therefore devoted more writing to explication and contextualizing.

>>>>

Our attempt at determining which verses enjoyed more consideration from the *mufassirūn* began with calculating the word count of every section of the *tafsīr* that was commenting on a specific verse and dividing that number by the total word count of the *tafsīr*. It was our belief that increased attention on a verse was indicative of some sort of importance to the *mufassir*. Importance might not necessarily mean that the *mufassir* had an increased affinity for the values or instructions espoused in the verse. A *mufassir* might have believed that an obscure verse required elucidation to make its message comprehensible to the Muslim layman and therefore devoted more writing to explication and contextualizing.
